Pillar 1 - Sequential Pattern Mining

### 2019-02-11 Pillar 1 - Sequential Pattern Mining.Rmd
list for sequences

  sequences <- data %>%
    filter(
      !is.na(eventID) #this is here casue we have courses that were never taken.
      ) %>% 
    group_by(
      sequenceID,
      eventID
    ) %>%
    summarise(
      list_item = list(!!enquo(item))
    ) %>%
    arrange(
      sequenceID,
      eventID
    ) %>%
    ungroup %>%
    pull(
      list_item
      ) %>%
    as("transactions")

@@

We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR,
     file = "App/AR.RDATA")

# Remove objects
rm(my_apriori, clean_AR, compute_metrics, edit_AR, make_AR,
   AR)
```

>>>>

  sequences <- data %>%
    filter(
      !is.na(eventID) #this is here casue we have courses that were never taken.
      ) %>% 
    group_by(
      sequenceID,
      eventID
    ) %>%
    summarise(
      list_item = list(unique(!!enquo(item)))
    ) %>%
    ungroup %>%
    arrange(
      sequenceID,
      eventID
    ) %>%
    pull(
      list_item
      ) %>%
    as("transactions")

@@

We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(
  AR,
  file = "App/AR.RDATA"
  )

# Remove objects
rm(
  my_apriori, clean_AR, compute_metrics, edit_AR, make_AR,
  AR
  )
```
